CFF GCT Study

### 2025-04-17 Christine Chan/CFF GCT Study/cff_gct_analysis.qmd
GCT CFRD + INDET

---
title: "CFF GCT Study"
author: "Tim Vigers"
date: "today"
date-format: long
format:
  html:
    toc: true
    toc-depth: 5
    toc-float: true
    code-fold: true
    self-contained: true
    fig-cap-location: top
    fig-height: 9
    fig-width: 12
    page-layout: full
    theme:
      light: flatly
      dark: darkly
bibliography: /home/timvigers/Documents/Miscellaneous/zotero.bib
csl: /home/timvigers/Documents/GitHub/styles/american-medical-association.csl
editor: source
---

@@

```{r}
#| label: tbl-roc-dysglycemia
#| tbl-cap: Accuracy of different screening tests to predict dysglycemia using ROC curve analyses
#| message: false
gctpl_roc <- roc(Dysglycemia ~ `GCT 60 min plasma`, data = df)
gctcap_roc <- roc(Dysglycemia ~ `GCT 60 min capillary`, data = df)
ogtt1_roc <- roc(Dysglycemia ~ `OGTT 60 min`, data = df)
rpg_roc <- roc(Dysglycemia ~ `GCT 0 min plasma`, data = df)
rcg_roc <- roc(Dysglycemia ~ `GCT 0 min capillary`, data = df)
a1c_roc <- roc(Dysglycemia ~ HbA1c, data = df)
roc_table <-
  lapply(
    list(gctpl_roc, gctcap_roc, ogtt1_roc, rpg_roc, rcg_roc, a1c_roc),
    function(roc) {
      coords(roc, "best", ret = "all")
    }
  )
roc_table <- do.call(rbind, roc_table)
rownames(roc_table) <- c("GCTpl", "GCTcap", "OGTT 1 hr", "RPG", "RCG", "A1c")
gt(roc_table, rownames_to_stub = T) %>% fmt_number(decimals = 3)
```

@@

@@

```{r}
#| label: tbl-roc-cfrd
#| tbl-cap: Accuracy of different screening tests to predict CFRD
#| message: false
gctpl_roc <- roc(CFRD ~ `GCT 60 min plasma`, data = df)
gctcap_roc <- roc(CFRD ~ `GCT 60 min capillary`, data = df)
ogtt1_roc <- roc(CFRD ~ `OGTT 60 min`, data = df)
rpg_roc <- roc(CFRD ~ `GCT 0 min plasma`, data = df)
rcg_roc <- roc(CFRD ~ `GCT 0 min capillary`, data = df)
a1c_roc <- roc(CFRD ~ HbA1c, data = df)
roc_table <-
  lapply(
    list(gctpl_roc, gctcap_roc, ogtt1_roc, rpg_roc, rcg_roc, a1c_roc),
    function(roc) {
      coords(roc, "best", ret = "all")
    }
  )
roc_table <- do.call(rbind, roc_table)
rownames(roc_table) <- c("GCTpl", "GCTcap", "OGTT 1 hr", "RPG", "RCG", "A1c")
gt(roc_table, rownames_to_stub = T) %>% fmt_number(decimals = 3)
```

@@

@@

>>>>

---
title: "CFF GCT Study"
author: "Tim Vigers"
date: "today"
date-format: long
format:
  html:
    toc: true
    toc-depth: 5
    toc-float: true
    code-fold: true
    self-contained: true
    fig-cap-location: top
    fig-height: 9
    fig-width: 12
    page-layout: full
editor: source
---

@@

```{r}
#| label: tbl-roc-dysglycemia
#| tbl-cap: Accuracy of different screening tests to predict dysglycemia using ROC curve analyses
#| message: false
gctpl_roc <- roc(Dysglycemia ~ `GCT 60 min plasma`, data = df)
gctcap_roc <- roc(Dysglycemia ~ `GCT 60 min capillary`, data = df)
ogtt0_roc <- roc(Dysglycemia ~ `OGTT 0 min`, data = df)
ogtt1_roc <- roc(Dysglycemia ~ `OGTT 60 min`, data = df)
rpg_roc <- roc(Dysglycemia ~ `GCT 0 min plasma`, data = df)
rcg_roc <- roc(Dysglycemia ~ `GCT 0 min capillary`, data = df)
a1c_roc <- roc(Dysglycemia ~ HbA1c, data = df)
roc_table <-
  lapply(
    list(gctpl_roc, gctcap_roc, ogtt0_roc, ogtt1_roc, rpg_roc, rcg_roc, a1c_roc),
    function(roc) {
      coords(roc, "best", ret = "all")
    }
  )
roc_table <- do.call(rbind, roc_table)
rownames(roc_table) <- c("GCTpl", "GCTcap", "OGTT 0 min", "OGTT 1 hr", "RPG", "RCG", "A1c")
gt(roc_table, rownames_to_stub = T) %>% fmt_number(decimals = 3)
```

@@

#### OGTT 0 min

```{r}
gt(data.frame(coords(ogtt0_roc, "all", ret = "all"))) %>%
  fmt_number(n_sigfig = 3)
```

@@

```{r}
#| label: tbl-roc-cfrd
#| tbl-cap: Accuracy of different screening tests to predict CFRD
#| message: false
gctpl_roc <- roc(CFRD ~ `GCT 60 min plasma`, data = df)
gctcap_roc <- roc(CFRD ~ `GCT 60 min capillary`, data = df)
ogtt0_roc <- roc(CFRD ~ `OGTT 0 min`, data = df)
ogtt1_roc <- roc(CFRD ~ `OGTT 60 min`, data = df)
rpg_roc <- roc(CFRD ~ `GCT 0 min plasma`, data = df)
rcg_roc <- roc(CFRD ~ `GCT 0 min capillary`, data = df)
a1c_roc <- roc(CFRD ~ HbA1c, data = df)
roc_table <-
  lapply(
    list(gctpl_roc, gctcap_roc, ogtt0_roc, ogtt1_roc, rpg_roc, rcg_roc, a1c_roc),
    function(roc) {
      coords(roc, "best", ret = "all")
    }
  )
roc_table <- do.call(rbind, roc_table)
rownames(roc_table) <- c("GCTpl", "GCTcap", "OGTT 0 min", "OGTT 1 hr", "RPG", "RCG", "A1c")
gt(roc_table, rownames_to_stub = T) %>% fmt_number(decimals = 3)
```

@@

```{r}
invisible(lapply(
  list(gctpl_roc, gctcap_roc, ogtt0_roc, ogtt1_roc, rpg_roc, rcg_roc, a1c_roc),
  function(roc) {
    print(plot(roc, print.auc = T, print.thres = T, legacy.axes = T))
  }
))
```

@@

## CFRD + INDET

CFRD + INDET was defined as a one hour OGTT $\geq$ 200 mg/dL OR two hour OGTT $\geq$ 200 mg/dL.

```{r}
df$CFRD_INDET <- factor(df$Diagnosis,
  levels = c("NGT", "IFG", "INDET", "IGT", "CFRD"),
  labels = c("No", "No", "Yes", "No", "Yes")
)
```

```{r}
#| label: tbl-roc-cfrd-indet
#| tbl-cap: Accuracy of different screening tests to predict CFRD + INDET
#| message: false
gctpl_roc <- roc(CFRD_INDET ~ `GCT 60 min plasma`, data = df)
gctcap_roc <- roc(CFRD_INDET ~ `GCT 60 min capillary`, data = df)
ogtt0_roc <- roc(CFRD_INDET ~ `OGTT 0 min`, data = df)
ogtt1_roc <- roc(CFRD_INDET ~ `OGTT 60 min`, data = df)
rpg_roc <- roc(CFRD_INDET ~ `GCT 0 min plasma`, data = df)
rcg_roc <- roc(CFRD_INDET ~ `GCT 0 min capillary`, data = df)
a1c_roc <- roc(CFRD_INDET ~ HbA1c, data = df)
roc_table <-
  lapply(
    list(gctpl_roc, gctcap_roc, ogtt0_roc, ogtt1_roc, rpg_roc, rcg_roc, a1c_roc),
    function(roc) {
      coords(roc, "best", ret = "all")
    }
  )
roc_table <- do.call(rbind, roc_table)
rownames(roc_table) <- c("GCTpl", "GCTcap", "OGTT 0 min", "OGTT 1 hr", "RPG", "RCG", "A1c")
gt(roc_table, rownames_to_stub = T) %>% fmt_number(decimals = 3)
```

```{r}
invisible(lapply(
  list(gctpl_roc, gctcap_roc, ogtt0_roc, ogtt1_roc, rpg_roc, rcg_roc, a1c_roc),
  function(roc) {
    print(plot(roc, print.auc = T, print.thres = T, legacy.axes = T))
  }
))
```

#### OGTT 0 min

```{r}
gt(data.frame(coords(ogtt0_roc, "all", ret = "all"))) %>%
  fmt_number(n_sigfig = 3)
```
